\documentclass[]{cvpn}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

%% 

\begin{document}

\cvheader{}

% Read 'git-rev.info' (which should contain the git rev)
% And insert into the \cvtag. Fallback to 'unknown'.
\IfFileExists{./git-rev.info}
     {\def\gitrev{\input{git-rev.info}\unskip}}
     {\def\gitrev{unknown}}
\cvtag{\gitrev}

\begin{multicols}{2}
\section{Work experience}
\begin{eventlist}

\item{Solution Architect ---\\Cloud, DevOps \& Security}
     {Slalom Build (Toronto)}
     {March '20 to Present}
{
Leading Cloud, DevOps \& Security technical
delivery on multiple client engagements.
Google Cloud subject-matter expert;
Slalom Build SRE working group.
}

\eventlink{}

\item{Senior Engineer ---\\Cloud, DevOps \& Security}
     {Slalom Build (Toronto)}
     {March '19 to March '20}
{
Delivered Cloud, DevOps \& Security competency on
multiple client engagements (telcos, media, finance).
Focus on delivery of pipelines and cloud solutions
for Data \& Analytics projects.
}

\item{Site Reliability Engineer}
     {Mercatus Technologies (Toronto)}
     {March '18 to Feb '19}
{
DevOps team.
Implemented Spinnaker,
built a data-driven anti-Web scrapper,
built a developer-centric PaaS on Kubernetes
(Rancher, EKS).
}

\item{Senior DevOps Developer}
     {500px (Toronto)}
     {March '17 to Nov '17}
{
Platform team.
Automation and architecting of platforms
(bare metal, Docker, AWS),
AWS migration. Chef, Terraform, Ansible.
}

\item{Senior Staff DevOps Engineer}
     {Achievers (Toronto)}
     {Sept '16 to Feb '17}
{
SRE team.
Automated (Chef) Jenkins platform for company-wide build
needs based on Jenkins Pipeline.
}

\item{DevOps Engineer}
     {shomi (Toronto)}
     {July '15 to Sept '16 (closed)}
{
DevOps team. As a bold team effort, moved shomi's
production from datacenter to cloud (AWS) in just 7 weeks.
Brought the team on board and implemented a technical
vision to automation (Terraform, Chef),
with a close collaboration with R\&D.
}

\item{DevOps Engineer}
     {Rakuten (Toronto)}
     {June '14 to July '15}
{
Rakuten Platform team, Global Operations.
Automated infrastructure and built a company-wide
standard platform using Chef.
}

\eventlink{}

\item{Build Engineer}
     {Rakuten Kobo (Toronto)}
     {August '12 to July '15}
{
Kobo operations / continuous integration (CI) team.
Created and managed CI pipelines.
Created REST-based deployment system (Bash, Python) \&
tools (Web, APIs, packaging, provisioning).
}

\item{Tech. Enablement Specialist}
     {IBM (Toronto)}
     {August '11 to May '12}
{
Created virtual appliances and images for IBM DB2.
}

\item{QA Analyst}
     {Neuralitic Systems (Montreal)}
     {June ‘10 to July ’11}
{
Introduced Neuralitic's first automated testing flow.
}

\end{eventlist}

\section{Main Skills}
\begin{skillslist}

\skill{Google Cloud Platform}{0.95}
\skill{Linux \& Scripting}{0.95}
\skill{Terraform}{0.9}
\skill{Python}{0.9}
\skill{Docker \& Compose}{0.9}
\skill{Kubernetes}{0.85}
\skill{Chef \& Ansible}{0.85}
\skill{Spinnaker \& CI tools}{0.85}
\skill{Amazon Web Services}{0.75}
\skill{Web (HTML/CSS/HTTP Stack)}{0.75}

\end{skillslist}

\section{Education}
\begin{eventlist}

\item{Bachelor of Engineering}
     {École de technologie supérieure (ÉTS)}
     {'03 to '09}
{
(Montreal) Information Technology Engineering.
}

\item{College Studies Diploma}
     {Collège de Bois-de-Boulogne}
     {'99 to '02}
{
(Montreal) Computer Science, network management.
}

\end{eventlist}

\section{Noteworthy}

% \subsection{Software team lead}
% \wherewhen{Eclipse Solar Car Team}{‘03 to ‘09}\\
% Built and raced two electric solar cars (US, Australia).
% Developed telemetry system (Java).\\

% TODO: Not sure why I need a \\ here.
% Otherwise there's no space before subsection.

% \subsection{Other}
% \wherewhen{CS Games}{’07 to ‘09, (’11 and ‘12 as alumni)}\\
% \wherewhen{Engineering Games}{‘08 to ’10 (’12 as director)}\\

\subsection{Sidelines \& Interests}
Travel, UX, design, touch screens, home automation,
trivia, architecture, tech talks, craft beer.

\end{multicols}
\end{document}