\documentclass[]{cvpn}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

%%

\begin{document}

\cvheader{}

% Read 'git-rev.info' (which should contain the git rev)
% And insert into the \cvtag. Fallback to 'unknown'.
\IfFileExists{./git-rev.info}
     {\def\gitrev{\input{git-rev.info}\unskip}}
     {\def\gitrev{unknown}}
\cvtag{\gitrev}

\begin{multicols}{2}
\section{Work experience}
\begin{eventlist}

\item{Senior Architect ---\\Cloud, DevOps \& Security}
{Slalom Build (Toronto)}
{July '21 to September '21}
{
     Lead Cloud, DevOps \& Security
     technical teams, client solution and delivery.
     Participate in RFP responses, business and CDS capability
     development. Google Cloud and Kubernetes subject-matter
     expert.
}

\eventlink{}

\item{Architect ---\\Cloud, DevOps \& Security}
     {Slalom Build (Toronto)}
     {March '20 to July '21}
{
     Lead Cloud, DevOps \& Security
     technical teams, client solution and delivery.
}

\eventlink{}

\item{Senior Engineer ---\\Cloud, DevOps \& Security}
     {Slalom Build (Toronto)}
     {March '19 to March '20}
{
     Delivered Cloud, DevOps \& Security competency
     on client engagements (telecom, media, finance, retail).
}

\item{Site Reliability Engineer}
     {Mercatus Technologies (Toronto)}
     {March '18 to Feb '19}
{
DevOps team.
Implemented Spinnaker,
built a data-driven anti-Web scrapper,
built a developer-centric PaaS on Kubernetes
(Rancher, EKS).
}

\item{Senior DevOps Developer}
     {500px (Toronto)}
     {March '17 to Nov '17}
{
Platform team.
Automated and architected platforms
(bare metal, Docker, AWS),
AWS migration. Chef, Terraform, Ansible.
}

\item{Senior Staff DevOps Engineer}
     {Achievers (Toronto)}
     {Sept '16 to Feb '17}
{
SRE team.
Automated (Chef) Jenkins platform for company-wide build
needs based on Jenkins Pipeline.
}

\item{DevOps Engineer}
     {shomi (Toronto)}
     {July '15 to Sept '16 (closed)}
{
DevOps team. As a bold team effort, moved shomi's
production from on-prem to cloud (AWS) in 7 weeks.
Brought the team on board and implemented a technical
vision to infrastruture automation (Terraform, Chef).
}

\item{DevOps Engineer}
     {Rakuten (Toronto)}
     {June '14 to July '15}
{
Rakuten Global Operations.
Automated infrastructure and built a company-wide
standard platform using Chef.
}

\eventlink{}

\item{Build Engineer}
     {Rakuten Kobo (Toronto)}
     {August '12 to July '15}
{
Kobo Operations team.
Created and improved build systems.
Created API-based deployment platform \& tools.
}

\item{Tech. Enablement Specialist}
     {IBM (Toronto)}
     {August '11 to May '12}
{
Created virtual appliances and images for IBM DB2.
}

\item{QA Analyst}
     {Neuralitic Systems (Montreal)}
     {June ‘10 to July ’11}
{
Introduced Neuralitic's first automated testing flow.
}

\end{eventlist}

\section{Main Skills}

\begin{skillslist}

\skill{Google Cloud}{0.95}
\skill{Terraform}{0.95}
\skill{Linux \& Scripting}{0.95}
\skill{Kubernetes}{0.85}
\skill{Python}{0.85}
\skill{Microsoft Azure}{0.65}
\skill{Amazon Web Services}{0.65}

\end{skillslist}

\section{Education}
\begin{eventlist}

\item{Bachelor of Engineering}
     {École de technologie supérieure (ÉTS)}
     {'03 to '09}
{
(Montreal) Information Technology Engineering.
}

\end{eventlist}

\section{Noteworthy}

\subsection{Technical Certifications}
Google Cloud (x8), Kubernetes (x2),\\Microsoft Azure (x2), HashiCorp (x2).
\\

% TODO: Not sure why I need a \\ here.
% Otherwise there's no space before subsection.

% \subsection{Software team lead}
% \wherewhen{Eclipse Solar Car Team}{‘03 to ‘09}\\
% Built and raced two electric solar cars (US, Australia).
% Developed telemetry system (Java).\\

% \subsection{Other}
% \wherewhen{CS Games}{’07 to ‘09, (’11 and ‘12 as alumni)}\\
% \wherewhen{Engineering Games}{‘08 to ’10 (’12 as director)}\\

\subsection{Sidelines \& Interests}
Travel, vintage Macs, design, home automation,
trivia, architecture, open source, tech talks.


\end{multicols}
\end{document}
